---
title: "Monitoring Changes In Data"
author: "Mark van der Loo and Edwin de Jonge"
date: "useR!2019"
output: 
  beamer_presentation:
    include:
      in_header: ../00tex/presheader.tex
classoption: "aspectratio=169"
---

## Try the code

\centering\huge

`03input/monitoring.R`

## How to monitor changes

### It depends $\ldots$

- Cell-by-cell changes?
- Count changes?
- Count changes in satisfying rules?
- Measure changes in aggregates?

## Decomposing the number of changes in cells

\centering
\includegraphics[height=5cm]{fig/cellsplit.pdf}

```{r, eval=FALSE}
validate::cells(start=dataset1, step1=dataset2, step3=dataset3, ...)
```


## Decomposing the number of changes in validation results

\centering
\includegraphics[height=5cm]{fig/rulesplit.pdf}

```{r, eval=FALSE}
validate::compare(rules, start=dataset1, step1=dataset2, ...)
```


## Assignment

1. Read all the versions of datasets created today
2. Create plots showing the progress in the cell counts and rule counts methods.




