---
title: "Error Localization"
author: "Mark van der Loo and Edwin de Jonge"
date: "useR!2019"
output: 
  beamer_presentation:
    include:
      in_header: ../00tex/presheader.tex
classoption: "aspectratio=169"
---

## Try the code

\centering\huge

`03valid/errorlocalization.R`

## Error localization


> Error localization is a procedure that points out fields in a
data set that can be altered or imputed in such a way that
all validation rules can be satisfied.


## Example

### Ruleset

```{r, eval=FALSE}
if (married == TRUE ) age >= 16
if (attends == "kindergarten") age <= 6
```

### Data

```{r, echo=FALSE}
knitr::kable(data.frame(age=3, married=TRUE, attends="kindergarten"))
```


### Question

Which field or fields would you change?

## Principle of Fellegi and Holt

###

Find the minimal (weighted) number of fields to adjust such that
all rules, including implied rules, can be satisfied.

\hfill{}\scriptsize{IP Fellegi and D Holt, JASA \textbf{71} 353  17--35 (1976).}

### Note

This should be used as a last resort, when no further information on 
the location of errors is available.


## Implied rules?

### 

```{r, eval=FALSE}
turnover - total.cost == profit
               profit <= 0.6 * turnover
```

This implies (substituting profit):

```{r, eval=FALSE}
           total.cost >= 0.4 * turnover
```

We need to take into account such _essentially new_ rules: a rule set forms
a system of rules and its implied rules. `errorlocate` takes this into account


## Choosing weights

### All weights equal (usually to one)

Least nr of variables adapted. In case of multiple solutions: choose randomly
(e.g. by adding a small random perturbation to the weights).

### Weights represent reliability

Heigher weight $\to$ variable is less likely chosen.

- Can be made to depend on 'outlierness', or expert judgement.
- Possible problem: minimal weights vs minimal nr of variables?

## errorlocate

`errorlocate` formulates a Mixed Integer Problem with:

 - `validate` rules set $R$ as a hard constraints

 - objective function: minimize 
 $$
 f(x_0, \delta) = \sum_{i} w_i \delta_i 
 $$
 with $\delta_i \in \{0,1\}$ and $\delta_i =  1$ 
 if field $i$ is an invalid value.
 
 - Penalize the number of fields 
 
## `locate_errors` and `replace_errors`

Find the errors:

```{r, eval = FALSE}
library(errorlocate)
errors <- locate_errors(data, rules)
```

Set the fields to `NA`:

```{r, eval = FALSE}
data_errors_to_na <- replace_errors(data, rules)
```


## Assignment

```{r, eval=FALSE}
# we first create a named weight vector with weight 1
weight <- rep(1, ncol(data_with_errors))
names(weight) <- names(data_with_errors)
```

- Set the weight of turnover to 10 and supply the weight to locate_errors
- Discuss the effect of setting te weight on turnover with your neighbor.
- Replace errors with `NA` using the `replace_errors` with the weights used above
- Store the results in "my_errors_located.csv".



