---
title: "Imputation"
author: "Mark van der Loo and Edwin de Jonge"
date: "useR!2019"
output: 
  beamer_presentation:
    include:
      in_header: ../00tex/presheader.tex
classoption: "aspectratio=169"
---

## Try the code

\centering\huge

`03valid/impute.R`

## Imputing data

### Need to specify

- Imputation method
- Variable(s) to impute
- Variables used as predictor

### Simputation's goal

Easy to experiment, robust enough for production.

### Simputation interface

```{r, eval=FALSE}
impute_<model>(data, imputed_variables ~ predictors, ...)
```


## Imputing data with simputation



|  `<model>  `      |  description                                    |
|-------------------|-------------------------------------------------|
| `proxy`           | copy (transformation of) other variable(s)      |
| `median`          | (group-wise) median                             |
| `rlm`, `lm`, `en` | (robust) linear model, elasticnet regression    |
| `cart`, `rf`      | Classification And Regression Tree, RandomForest|
| `em`, `mf`        | EM-alogithm (multivariate normal) `missForest`  |
| `knn`             | $k$ nearest neighbours                          |
| `shd`, `rhd`      | sequential, random, hot-deck                    |
| `pmm`             | predictive mean matching                        |
| `impute_model`    | use pre-trained model                           |



## Imputation of the mean

```{r,echo=FALSE, fig.height=5.5}
library(magrittr)
library(simputation)
par(mfrow=c(1,2))
X <- rnorm(1000)
Y <- X + rnorm(1000,sd = 0.2)
i <- sample(1:1000,100,replace=FALSE)
Y[i] <- NA
plot(X,Y,pch=".",main="10% missing in Y", las=1)
d <- data.frame(X=X,Y=Y)
library(simputation)
d1 <- impute_lm(d,Y ~ X)
cols <- rep("black",1000)
cols[i] <- "red"
cex <- rep(1,1000)
cex[i] <- 4
plot(Y ~ X, data=d1, col=cols,pch=".",cex=cex,las=1,main="Imputation with model Y = a + bX")
```


## Adding a random residual

```{r, echo=FALSE, fig.height=5.5}
data("retailers", package="validate")
library(magrittr)
library(simputation)
ret <- retailers[3:10]
par(mfrow=c(1,2))
cols <- rep("black",1000)
cols[i] <- "red"
cex <- rep(1,1000)
cex[i] <- 3
plot(Y ~ X, data=d1, col=cols,pch=".",cex=cex,las=1,main="Imputation with model Y = a + bX")

d2 <- impute_lm(d,Y ~ X,add_residual = "normal")
plot(Y ~ X, data=d2, col=cols,pch=".",cex=cex,las=1,main="Imputation with Y = a + bX + e")
```




## Adding a random residual with `simputation`

### Example

```{r, echo=FALSE, results='hide'}
companies <- read.csv("../../02input/errors_located.csv"
                      , stringsAsFactors=FALSE)
```

```{r, results='hide'}
impute_rlm(companies, other.rev ~ turnover
         , add_residual = "normal") 
```

### Options

-  "none"`: (default)
-  "normal"`: from $N(0,\hat{\sigma})$ 
-  "observed"`: from observed residuals

## Chaining methods

### Example

```{r, results='hide'}
companies %>%
  impute_lm(turnover ~ staff + profit) %>%
  impute_lm(turnover ~ staff)
```

## Assignment

1. Read `errors_located.csv` (`stringsAsFactors=FALSE`)
2. Make a separete data frame, selecting columns 11--14 (`staff`--`vat`)
3. Implement the following imputation sequence:
    - Impute `turnover` by copying the `vat` variable (`impute_proxy`)
    - Impute `staff` with a robust linear model based on `staff.costs`
    - Impute `staff` with a robust linear model based on `total.costs`
    - Impute `profit` as `total.rev - total.costs` (`impute_proxy`)
    - Impute everything else using `missForest` (formula: `. ~ .`)







