---
title: "Data Validation"
author: "Mark van der Loo and Edwin de Jonge"
date: "useR!2019"
output: 
  beamer_presentation:
    include:
      in_header: ../00tex/presheader.tex
classoption: "aspectratio=169"
---


## Try the code

\centering\huge

`03valid/make_valid.R`


## Data validation

Verify that data satisfy technical restrictions and does not contradict
expert knowledge.


### Examples of technical demands

- Number of records must equal 60
- Financial variables are numeric
- Records have a unique `id`
- Zipcode consists of 4 numbers followed by 2 letters 

### Examples of domain knowledge demands

- turnover is nonnegative
- turnover $-$ costs $=$ profit
- profit not larger then 60\% of turnover
- average profit is larger than 0
- average profit differs less than 10% from last year's average

## Data validation rules

A domain specific language to express demands.

### Why?

- Communicate data quality without ambiguities
- Make knowledge explicit and organize it
- Create custom data quality reports
- Reuse ruleset for data cleaning purposes

### How?

```{r, eval=FALSE}
library(validate)
companies <- read.csv("02input/input.csv",stringsAsFactors = FALSE)
rules     <- validator(.file="02input/rules.R")
result    <- confront(companies, rules)
```

## Core concepts of the `validate` package


\begin{center}
\includegraphics[height=90mm]{fig/diagram.png}
\end{center}

## Overview of the work flow

\begin{center}
\includegraphics[height=50mm]{fig/overview.pdf}
\end{center}


## Data validation: informal definitions

### Data validation

Check if a value, or combination of values is in a certain set
of valid values or valid value combinations.

### Data validation language in `validate`

Any R expression that results in a `logical`.

## Expressions that are validation rules

### Basic syntax

- Any type check: `is.numeric`, `is.character`,$\ldots$
- Any comparison: `<, <=, ==, identical !=, %in%, >=, >`
- Logical operators `|, &, if, !, all, any`
- Pattern match: `grepl`


### Sugar

Dot "`.`" stands for the whole data set:
```{r, eval=FALSE}
nrow(.) >= 50       # at least 40 rows
"id" %in% names(.)  # 'id' must be present
```

More, see `?syntax` or `vignette("introduction", package="validate")`


## Challenges

1. Express the following restrictions on `companies`. Then, `confront`, and `summarize`
    - Profit does not exceed 60% of turnover
    - turnover less costs equals profit
    - Average profit is larger than zero
    - correlation (`corr`) between total cost and staff exceeds 0.5
    - zipcode is 4 numbers followed by two upper case letters (you need to know regex)
2. Copy those rules in a separate file `myrules.R`. Read into a `validator`.

















